%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}

\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\name{Wesley Tian} % Your name
\address{{413~$\cdot$~636~$\cdot$~6304} \\ {5 Valley Ln} \\ {Amherst, MA 01002}}
\address{\href{mailto:wesley.tian@icloud.com}{wesley.tian@icloud.com} \\ \href{http://wesleytian.com/}{wesleytian.com} \\ \href{http://github.com/wesleytian}{github.com/wesleytian}}

\begin{document}
	
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	

	\begin{rSection}{Education}
		{\bf University of Michigan} \hfill {Apr. 2019} \\ 
		B.S. in Computer Science \hfill {Ann Arbor, MI}
		
		{\bf University of Massachusetts Amherst} \hfill {Sep. 2015 - May 2017} \\ 
		B.S. in Computer Science \& B.S. in Mathematics \hfill {Amherst, MA} \\
		GPA: 3.76 / 4.00 \smallskip \\
		Courses: Programming w/ Data Structures, Programming Methodology, Computer Systems Principles, Reasoning Under Uncertainty, Intro to Computation, A.I., Calculus I, II \& III, Linear Algebra, Game Theory
		
		\textbf{Edx.org $/$ Coursera.org} \\
		Courses: Machine Learning, Learning How to Learn
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	% AWARDS SECTION
	%----------------------------------------------------------------------------------------
	
	%\begin{rSection}{Awards}
	%	- Most Creative Use of Indico API at Hamp Hack (2017) \\
	%	- Commonwealth Honors College (2016, 2017) \\
	%	- Dean's List Honors (2015, 2016, 2017) \\
	%	- Chancellor's Scholarship (2015)
	%\end{rSection}
	
	%----------------------------------------------------------------------------------------
	% EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{EXPRERIENCE}
			
		\begin{rSubsection}{Fidelity Investments Inc.} {May 2017 - Present}{Software Engineering Intern}{Merrimack, NH}
			\item Working on NetBenefits web application
		\end{rSubsection}
	
		\begin{rSubsection}{RaysHobby LLC} {May 2016 - May 2017}{Intern}{Amherst, MA}
			\item Designed, assembled and tested embedded circuits and home automation gadgets
			\item Invented product while working with Prof. Rui Wang on open-source software/hardware business
			\item Soldered components and developed firmware in C++ for Thermostat Pro
		\end{rSubsection}
	
		\begin{rSubsection}{XuanLiang Co. Ltd.} {Jan. 2015 - Feb. 2015}{R\&D  Intern}{Shanghai, China}
			\item Tested and debugged Android games with over 1 million downloads
			\item Supported in conceiving new software features
			\item Collaborated in Java with 10 other team members while communicating in foreign language
		\end{rSubsection}
	
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	PROJECTS SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{PROJECTS}
	
		\begin{rSubsection}{FashionFiltr}{Apr. 2017}{Web application $\cdot$ {\href{https://devpost.com/software/fashion-filtr}{devpost.com/software/fashion-filtr}}}{Amherst, MA}
			\item Applied state-of-the-art deep learning models to help users narrow down choices when shopping for clothes online
			\item Trained machine learning models using Indico API and hosted web application using AWS' EC2 instance
			\item Coded in 24 hours with 2 colleagues, won Indico sponsored prize and awarded a total of $\$$3000 in API credits	
		\end{rSubsection}
	
		\begin{rSubsection}{Thermostat Pro}{Aug. 2016}{Internet of things (IoT) \& mobile application $\cdot$ {\href{https://github.com/wesleytian/thermostat-pro}{github.com/wesleytian/thermostat-pro}} }{Amherst, MA}
			\item Detects room temperature and regulates it by controlling RF signal output sent to a remote power socket that your air conditioner or heater is plugged into
			\item Programmed firmware using C++, built using Arduino and spare components at RaysHobby's workshop
			\item Mobile app interfaces Thermostat Pro and allows user to monitor room temperature and schedule air conditioner or heater as well as control other settings
			\item Developed app using cross-platform hybrid Ionic framework for front-end and Blynk API for server
		\end{rSubsection}
	\end{rSection}
	
	\begin{rSection}{Skills}
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
		Languages & Java, C, C++, Scala, Python, Bash, HTML5, CSS3, JavaScript, Octave \\ 
		Frameworks \& Platforms & Node.js, Ionic, AngularJS, Apache Cordova\\
		APIs & jQuery, Blynk, Google Maps, Indico \\
		Other & Git, \LaTeX, Mandarin Chinese
		\end{tabular}
	\end{rSection}
	
\end{document}